---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
data<-read.csv( "RepData_PeerAssessment1/activity.csv")
```


## What is mean total number of steps taken per day?

For this part of the assignment, missing values in the dataset are ignored.

1. Make a histogram of the total number of steps taken each day

```{r}
Steps_daycount <- as.data.frame(unlist(lapply(daily_data,function(x) sum(x[,c("steps")]))))[,1]
hist(Steps_daycount)

```

2.Calculate and report the mean and median total number of steps taken per day

```{r}
Steps_daymean <- as.data.frame(unlist(lapply(daily_data,function(x) mean(x[,c("steps")]))))[,1]
Steps_daymedian <- as.data.frame(unlist(lapply(daily_data,function(x) median(x[,c("steps")]))))[,1]
Mean_Median_days<-cbind(unique(data$date),Steps_daymean,Steps_daymedian)
colnames(Mean_Median_days) <- c("day","mean","median")
Mean_Median_daysdata
```


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
